Attrition in Online Learning: Understanding Persistence and Dropout in Massive Open Online Courses

### 2014-10-28 paper_v1.Rnw
more restructuring

@@

Attrition can be a sign of success if a learner has achieved their personal goal. We therefore investigated what proportion of learners who dropped out were satisfied with their achievements in the course (RQ2). TODO add satisfaction analysis here

>>>>

\subsubsection{Predictors}

RQ1: How do prior learner characteristics (demographics, geographic location, enrollment intentions, and previous online courses) influence learners' likelihood of disengaging from a MOOC?

TODO Rene adds these analyses here

\subsubsection{Satisfaction}

RQ2a: What proportion of learners who disengaged were satisfied with their achievements in the course?

RQ2b: How does learners' behavior in the MOOC vary by their level of satisfaction?

Attrition can be a sign of success if a learner has achieved their personal goal. We therefore investigated what proportion of learners who dropped out were satisfied with their achievements in the course (RQ2).

TODO Sherif adds satisfaction analyses here

\subsubsection{Reasons}

RQ3a: What reasons do learners report for disengaging from a MOOC?

RQ3b: How do reasons for disengaging vary across prior learner characteristics (cf. RQ1)?

@@
